With the opXRD database, a curation of $\numpatterns$ unlabeled and 2179 at least partially labeled experimental powder X-ray diffraction patterns from a wide range of different materials systems, we provide the largest currently available source of experimental XRD patterns. With this, we address the need for experimental data that arises when developing algorithms and analysis tools for pXRD data, both based on machine learning and classical approaches. The data can be used for the actual method development and for testing. Our dataset is a valuable and so far missing resource to drive further developments in the automated analysis of XRD data. \added{Looking forward, opXRD is expected to play an important role in the development of advanced transfer learning approaches that integrate large-scale simulated data with real experimental patterns, ultimately driving the automation and accuracy of pXRD analysis. Future work will also include comprehensive benchmark evaluations to quantify the performance improvements achieved by incorporating opXRD into transfer learning pipelines.}

% How to contribute
Rather than a finished project, the opXRD database is an ongoing effort to collect experimental powder XRD data. We invite everyone \deleted{who is} working in the area of experimental powder XRD to submit it to the dataset, \deleted{in order} to further improve the utility of the dataset and thus aid further developments in this field. Our submission page (\url{https://xrd.aimat.science/}) \deleted{and submission helper software} will \replaced{continue to stay}{ be kept available} \added{available for the submission of data. As new submissions come in, newer versions of the opXRD database incorporating these submitted datasets will be released.}
\added{As the opXRD database grows further, we look forward to expanding this website to become a comprehensive community resource from which the database can be governed. Planned resources on this site include a contributor list, version list, and changelogs as well as comprehensive versioning, license, citation, and attribution practice statements. }

We will keep updating and maintaining the dataset with new incoming submissions.
